\huge A Usability Evaluation of Tor Launcher

### 2016-11-15 pets2017-paper/pets2017-paper.tex
fix summative demographics

\subsection{Recruitment}
We recruited people from Craigslist using the recruitment text in Appendix~\ref{qualitative-recruitment}, which linked an prescreening survey that collected demographics (Appendix~\ref{qualitative-prescreening}). We pre-screened~\cite{screening} for diversity in gender, age, technical expertise, use of security tools, and familiarity with Tor in a small participant pool. Of our 16 recruited participants, 50\% were male. Ages ranged from 20 to~62 years ($\mu = 30.5$, $\sigma = 13.5$). One participant declined to submit their age, so the previous calcuations were done without thier information. 100\% had at least some college education. We took participants' self-reported familiarity with technical terms use of security tools with skepticism (Appendix~\ref{prescreening-responses}). We verified their self-reported familiarity with Tor Browser in-person, and found that 4 used it, 3 heard of it but not used it, and the remaining 9 never heard of or used it. The main objective of this question was to identify new users versus infrequent users. We considered participants who had never heard of Tor or have only heard of Tor to be new users and those who have used Tor to be previous users.

@@

{\color {red} Of our recruited 124 participants, 56.8\% were male. Ages ranged from 18 to~68 years ($\mu = 28.9$, $\sigma = 12$). 56.8\% were male. 84.8\% of our participants had a college education.} We distributed participants evenly across experimental condition, about 20 in each interface and environment combination. Although there is variation in gender and age in each experimental condition, we ensured each condition had about half Craigslist recruited participants and half <redacted lab>  pool participants.

@@

\subsection{Results} 
124 people participated in our experiment, but we used data from 114. We filtered participants who made errors in completing the consent form, did not understand the task, or did not interact with the instrumented interface. In this section, we use OLD to refer to the deployed Tor Browser 5.0.3 Tor Launcher GUI (Figure~\ref{fig:old-interface}) and NEW to refer to our redesigned version (Figure~\ref{fig:new-interface}). Table~\ref{table:participant-summary} gives an overview of the results and Figure~\ref{fig:all-participant-edges} summarizes all participants' paths during the experiment.

\begin{table}[t]
\centering
\begin{tabular}{l r r r r r}
& \multicolumn{2}{r}{completion rate} & \multicolumn{1}{r}{connection} & \multicolumn{1}{r}{configuration} \\
& \multicolumn{2}{r}{(at 40min 8s)} & \multicolumn{1}{r}{time (med)} & \multicolumn{1}{r}{time (med)} \\
\noalign{\hrule}
E1-NEW & 19/19 & 100\% & 0:20 & 0:06 \\
E1-OLD & 19/19 & 100\% & 1:01 & 0:24 \\
E2-NEW & 18/18 & 100\% & 3:22 & 0:40 \\
E2-OLD & 16/19 & 84\% & 5:00 & 2:04 \\
E3-NEW & 13/19 & 68\% & 20:25 & 1:56 \\
E3-OLD & 10/20 & 50\% & 40:08 & 9:09 \\
\end{tabular}
\caption{
An overview of the results of the experiment. Those who
failed to connect were assigned the maximum time of 40:08.
}
\label{table:participant-summary}
\end{table}

>>>>

\subsection{Recruitment}
We recruited people from Craigslist using the recruitment text in Appendix~\ref{qualitative-recruitment}, which linked an prescreening survey that collected demographics (Appendix~\ref{qualitative-prescreening}). We pre-screened~\cite{screening} for diversity in gender, age, technical expertise, use of security tools, and familiarity with Tor in a small participant pool. Of our 16 recruited participants, 50\% identified as male and 50\% identified as female. Ages ranged from 20 to~62 years ($\mu = 30.5$, $\sigma = 13.5$). One participant declined to submit their age, so the previous calcuations were done without thier information. 100\% had at least some college education. We took participants' self-reported familiarity with technical terms use of security tools with skepticism (Appendix~\ref{prescreening-responses}). We verified their self-reported familiarity with Tor Browser in-person, and found that 4 used it, 3 heard of it but not used it, and the remaining 9 never heard of or used it. The main objective of this question was to identify new users versus infrequent users. We considered participants who had never heard of Tor or have only heard of Tor to be new users and those who have used Tor to be previous users.

@@

Of our recruited 124 participants, 44.2\% identified as male, 54.0\% identified as female, and 1.8\% identified as neither. Ages ranged from 18 to~68 years ($\mu = 28.2$, $\sigma = 12.3$). 84.1\% of our participants had at least a college education. We distributed participants evenly across experimental condition, about 20 in each interface and environment combination. Although there is variation in gender and age in each experimental condition, we ensured each condition had about half Craigslist recruited participants and half <redacted lab>  pool participants.

@@

\subsection{Results} 
124 people participated in our experiment, but we used data from 113. We filtered participants who made errors in completing the consent form, did not complete the exit survey, did not understand the task, or did not interact with the instrumented interface. In this section, we use OLD to refer to the deployed Tor Browser 5.0.3 Tor Launcher GUI (Figure~\ref{fig:old-interface}) and NEW to refer to our redesigned version (Figure~\ref{fig:new-interface}). Table~\ref{table:participant-summary} gives an overview of the results and Figure~\ref{fig:all-participant-edges} summarizes all participants' paths during the experiment.

\begin{table}[t]
\centering
\begin{tabular}{l r r r r r}
& \multicolumn{2}{r}{completion rate} & \multicolumn{1}{r}{connection} & \multicolumn{1}{r}{configuration} \\
& \multicolumn{2}{r}{(at 40min 8s)} & \multicolumn{1}{r}{time (med)} & \multicolumn{1}{r}{time (med)} \\
\noalign{\hrule}
E1-NEW & 19/19 & 100\% & 0:20 & 0:06 \\
E1-OLD & 19/19 & 100\% & 1:01 & 0:24 \\
E2-NEW & 18/18 & 100\% & 3:22 & 0:40 \\
E2-OLD & 16/19 & 84\% & 5:00 & 2:04 \\
E3-NEW & 13/19 & 68\% & 20:25 & 1:56 \\
E3-OLD & 10/20 & 50\% & 40:08 & 9:09 \\
\end{tabular}
\caption{
An overview of the results of the experiment. Those who
failed to connect were assigned the maximum time of 40:08, 
the maximum time a participant took to finish the task.
}
\label{table:participant-summary}
\end{table}
